Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
add refs
update table

The speed and thickness of a laminar helium flame are determined by the
energy generation rate and conductivity, and scale roughly as 
\begin{equation}
v_f \approx \sqrt{k_\mathrm{th} \dot{\epsilon}}
\end{equation}
and
\begin{equation}
\lambda_f = \sqrt{\frac{k_\mathrm{th}}{\dot{\epsilon}}}
\end{equation}
\citep{orourke:1979}.
At the densities we consider in this simulation, the pure He flame
speed is quite slow and would require a prohibitively long integration
time to see significant evolution of the burning.  We therefore
consider boosted flames in this first paper, to accelerate the burning
and allow us to understand the qualitative effects of laterally
propagating flames.  To boost the flame, while keeping the thickness
the same, we can multiply both the burning rate and the conductivity
by the same factor.  For our standard calculations, we choose 10 for
each, to give a flame 10$\times$ faster.  We call this the ``10/10''
flame.  We will also do a simulation with the reactions and
conductivity both boosted by 5, the ``5/5'' flame.

@@

Things to try to make the model feasible:
\begin{itemize}
\item Start the initial perturbation location near the Rossby radius
\item Hotter ``hot'' model
\item Aprox13
\item Higher diffusion cutoff lessens the timestep restriction
\end{itemize}

@@

\begin{deluxetable}{lccccc}
\tablecaption{\label{table:sim_names} Simulation parameters.}
\tablehead{\colhead{name} & \colhead{reaction boost} & \colhead{conductivity boost} & \colhead{fine grid resolution} & \colhead{rotation rate}  & \colhead{network}}
\startdata
10/10 & 10 & 10 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10-slow & 10 & 10 & 10~cm & 1000~Hz & {\tt aprox13} \\
10/10-lores & 10 & 10 & 20~cm & 2000~Hz & {\tt aprox13} \\
5/5 & 5 & 5 & 10~cm & 2000~Hz & {\tt aprox13} \\
10/10-iso7 & 10 & 10 & 10~cm & 2000~Hz & {\tt iso7} \\
\enddata
\end{deluxetable}

@@

% made with overview.py
\begin{figure}[h]
\centering
\plotone{flame_boost_10_10_overview}
\caption{\label{fig:10_10_overview} Temperature, energy generation rate, and out-of-plane velocity for the 10/10 simulation.}
\end{figure}

>>>>

The speed and thickness of a laminar helium flame are determined by the
energy generation rate and conductivity, and scale roughly as 
\begin{equation}
v_f \approx \sqrt{k_\mathrm{th} \dot{\epsilon}} \qquad
\lambda_f \approx \sqrt{\frac{k_\mathrm{th}}{\dot{\epsilon}}}
\end{equation}
\citep{orourke:1979,khokhlov:1993}.
At the densities we consider in this simulation, the pure He flame
speed is quite slow and would require a prohibitively long integration
time to see significant evolution of the burning.  We therefore
consider boosted flames in this first paper, to accelerate the burning
and allow us to understand the qualitative effects of laterally
propagating flames.  To boost the flame, while keeping the thickness
the same, we can multiply both the burning rate and the conductivity
by the same factor.  For our standard calculations, we choose 10 for
each, to give a flame 10$\times$ faster.  We call this the ``10/10''
flame.  We will also do a simulation with the reactions and
conductivity both boosted by 5, the ``5/5'' flame.

@@

@@

\begin{deluxetable}{lcccccc}
\tablecaption{\label{table:sim_names} Simulation parameters.}
\tablehead{\colhead{name} &
           \colhead{reaction} &
           \colhead{conductivity} &
           \colhead{fine grid} &
           \colhead{rotation} &
           \colhead{domain size} &
           \colhead{network} \\
%
           \colhead{} &
           \colhead{boost} &
           \colhead{boost} &
           \colhead{resolution} &
           \colhead{rate} &
           \colhead{} &
           \colhead{}
}
\startdata
10/10 & 10 & 10 & 10~cm & 2000~Hz & $1.2288\times 10^5~\mbox{cm} \times 3.072\times 10^4~\mbox{cm}$ & {\tt aprox13} \\
10/10-slow & 10 & 10 & 10~cm & 1000~Hz & $1.8432\times 10^5~\mbox{cm} \times 3.072\times 10^4~\mbox{cm}$ &{\tt aprox13} \\
10/10-lores & 10 & 10 & 20~cm & 2000~Hz & $1.2288\times 10^5~\mbox{cm} \times 3.072\times 10^4~\mbox{cm}$ &{\tt aprox13} \\
5/5 & 5 & 5 & 10~cm & 2000~Hz & $1.2288\times 10^5~\mbox{cm} \times 3.072\times 10^4~\mbox{cm}$  &{\tt aprox13} \\
10/10-iso7 & 10 & 10 & 10~cm & 2000~Hz & $1.2288\times 10^5~\mbox{cm} \times 3.072\times 10^4~\mbox{cm}$ &{\tt iso7} \\
\enddata
\end{deluxetable}

@@

% made with overview.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_overview}
\caption{\label{fig:10_10_overview} Temperature, energy generation rate, and out-of-plane velocity for the 10/10 simulation.}
\end{figure}

% made with slice_multi_crop.py
\begin{figure}[h]
\centering
\plotone{flame_wave_boost_10_10_lowres_slice}
\caption{\label{fig:10_10_lowres} Temperature, mean molecular weight, energy generation rate, and out-of-plane velocity for the 10/10 low resolution simulation.}
\end{figure}
